Fail Faster

### 2025-03-17 paper/paper.tex
pbt for pbt

\subsection{Implementing and Testing Generators}
\label{subsection:pbt-for-pbt}
\jwc{Talk about the difftesting to ensure staging maintains semantics, and also different RNGs have identical semantics.}
\subsection{Benchmarking speed \& resource usage}

\jwc{NOTE: we should test generator speed across both languages, but speed -> bugfinding ability in only OCaml.}
\jwc{
  Baseline generators to test speed in both languages:
  \begin{itemize}
    \item Single int
    \item Pair of ints, constrained
    \item List of ints without bind (use map): lots of sampling, minimal binds.
    \item Unableled Trees of a fixed size (no weighted union) minimal sampling, lots of binds.
  \end{itemize}
}
\subsection{Impact on bug-finding ability}
We evaluate the bug-finding ability of three of our case studies---BST, RBT, and STLC---using Etna, a platform for assessing and comparing property-based testing (PBT) techniques. 
Etna allows users to measure the effectiveness of different generator implementations by injecting bugs into the system under test and recording the time until a relevant 
property fails in response. For example, in a tree with a property ensuring that the tree remains ordered, a bug might involve inserting a value that violates that ordering. 
A \textit{task} consists of a bug-property pair, and each case study is associated with a diverse set of tasks that exercise different parts
of the system. In particular, BST has 30 tasks, RBT has 46 tasks, and STLC has 18 tasks.

>>>>

\subsection{Implementing and Testing Generators}
\label{subsection:pbt-for-pbt}
To establish the equivalence of generators up to program equality, we use a PBT harness to compare their outputs. 
Specifically, we generate random (size, seed) pairs and evaluate whether the generators under test produce equal results. 
If the equality property fails, we report the unequal trees; if, over 1,000 trials, no ``counterexample'' is reported, we consider the
behavior of the generators to be equivalent.
\subsection{Benchmarking speed \& resource usage}

\jwc{NOTE: we should test generator speed across both languages, but speed -> bugfinding ability in only OCaml.}
\jwc{
  Baseline generators to test speed in both languages:
  \begin{itemize}
    \item Single int
    \item Pair of ints, constrained
    \item List of ints without bind (use map): lots of sampling, minimal binds.
    \item Unableled Trees of a fixed size (no weighted union) minimal sampling, lots of binds.
  \end{itemize}
}
\subsection{Impact on bug-finding ability}
We evaluate the bug-finding ability of three of our case studies---BST, RBT, and STLC---using Etna, a platform for assessing and comparing property-based testing (PBT) techniques. 
Etna allows users to measure the effectiveness of different generator implementations by injecting bugs into the system under test and recording the time until a relevant 
property fails in response. For example, in a tree with a property ensuring that the tree remains ordered, a bug might involve inserting a value that violates that ordering. 
Each case study includes a diverse set of \textit{tasks}, where a task consists of a specific bug-property pair designed to test different aspects of the system.
